---
title: "homework1"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Загрузка необходимых библиотек
```{r}
library(dplyr)
library(ggplot2)
library(skimr)
library(tidyr)
library(purrr)
library(ggpubr)
#install.packages("wesanderson")
library(wesanderson)
```
<br>
#Загрузка дата-сета
<br>
```{r}
insurance_cost <- read.csv('insurance_cost.csv', stringsAsFactors = T)
head(insurance_cost)
```
```{r}
skim(insurance_cost)
```
<br>
#Вывод гистограммы всех нумерических переменных.
<br>
```{r}
insurance_cost %>%
  keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram(bins = 20) +
    theme_light()
```
<br>
#График плотности по колонке charges.
<br>
```{r}
mean <- round(mean(insurance_cost$charges),1)
median <- round(median(insurance_cost$charges),1)

ch_density <-insurance_cost %>%
  ggplot() +
  geom_density(aes(x = charges)) +
  geom_vline(aes(xintercept = mean), color = "blue") +
  annotate("text", 
           x= mean+6000, 
           y = 4e-05, 
           label=paste0("Mean=", mean), color = "blue") +
  geom_vline(aes(xintercept = median), color = "magenta") +
  annotate("text", 
           x= median+6000, 
           y = 5e-05, 
           label=paste0("Median=", median), color = "magenta") +
  ggtitle("Charges density chart") +
  labs(x = "Ameuwnt of charges", y = "Density") +
  theme_bw()

ch_density
```
<br>
#Ящик с усами по отношению переменных charges и (1) sex (2) smoker (3)  region.
```{r}
ch_sex <- insurance_cost %>%
  ggplot()+
  geom_boxplot(aes(x = charges, y = sex)) + 
  labs(x = "Charges", y = "Sex") +
  theme_bw()
ch_sex

ch_smoker <- insurance_cost %>%
  ggplot()+
  geom_boxplot(aes(x = charges, y = smoker)) + 
  labs(x = "Charges", y = "Whether they smoke or not") +
  theme_bw()
ch_smoker

ch_region <- insurance_cost %>%
  ggplot()+
  geom_boxplot(aes(x = charges, y = region)) + 
  labs(x = "Charges", y = "Region") +
  theme_bw()
ch_region
```
<br>
#Объединение "ящиков с усами" и графика плотности
<br>
```{r}
boxes <- ggarrange(ch_sex, ch_smoker, ch_region, ncol = 3, nrow = 1)
combined_plots <-ggarrange(ch_density, boxes, ncol = 1, nrow = 2)
annotate_figure(combined_plots, top = text_grob("Chharges, their density and how they vary depending on sex, region and smoking", size = 13, face = "bold"))
```
<br>
#Фасет графика из задания 3 по колонке region
<br>
```{r}
ch_density + facet_wrap(.~region)
```
<br>
#Scatter plot отношения переменных age и charges
<br>
```{r}
scatterplot <- insurance_cost %>%
  ggplot() + 
  geom_point(aes(x = age, y = charges)) +
  ggtitle("Dependance of the charges amount on age") +
  labs(x = "Age", y = "Charges") +
  theme_bw()
scatterplot + theme(axis.text.x = element_text(size = 14)) 

```
<br>
#Линия тренда для предыдущего графика
<br>
```{r message=FALSE}
insurance_cost %>%
  ggplot(aes(x = age, y = charges)) + 
  geom_point() +
  geom_smooth(method = lm, 
              color = "magenta", 
              fullrange = T,
              fill = "blue",
              se = TRUE,
              size = 0.5) +
  ggtitle("Dependance of the charges amount on age") +
  labs(x = "Age", y = "Charges") +
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14)) 
```
<br>
#Разбивка предыдущего графика по колонке smokers
<br>
```{r}
insurance_cost %>%
  ggplot(aes(x = age, y = charges, color = smoker, fill = smoker, group = smoker)) + 
  geom_point() +
  geom_smooth(method = lm, 
              color = "magenta", 
              fullrange = T,
              fill = "blue",
              se = TRUE,
              size = 0.5) +
  ggtitle("Dependance of the charges amount on age") +
  labs(x = "Age", y = "Charges") +
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14))
```
<br>
#Вместо переменной age  переменная bmi
<br>
```{r}
insurance_cost %>%
  ggplot(aes(x = bmi, y = charges, color = smoker, fill = smoker, group = smoker)) + 
  geom_point() +
  geom_smooth(method = lm, 
              color = "magenta", 
              fullrange = T,
              fill = "blue",
              se = TRUE,
              size = 0.5) +
  ggtitle("Dependance of the charges amount on BMI") +
  labs(x = "BMI", y = "Charges") +
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14))
```
<br>
#Вопросы к данным
<br>

##Вопрос №1.

<br>

Does BMI tends to increase if a person smokes?

<br>

Let's make a box-plot to have a look at BMI and how it varies as it would be more informative

<br>
```{r message = FALSE}
insurance_cost %>%
  filter(smoker == 'yes') %>%
  ggplot(aes(x = bmi, y = sex)) +
  geom_boxplot() +
  labs(y = "sex", x = "BMI") +
  ggtitle("BMI, sex, smoking") +
  theme_bw() +
  coord_flip() 
  
```
<br>

**Looking at the graphs, we can conclude that the BMI of smokers does not differ significantly by gender, however, the median value in both cases corresponds to preobesity.**

<br>
##Вопрос №2
<br>
Is there any dependance on the charges if a woman has kids
```{r}
insurance_cost$has_children <- ifelse(insurance_cost$children == 0, "no","yes")
insurance_cost$has_children <- factor(insurance_cost$has_children, levels = c('yes' , 'no'))
insurance_cost %>%
  filter(sex == "female") %>%
  
  ggplot(aes(x = age, y = charges, color = has_children, fill = has_children, group = has_children)) + 
  geom_point() +
  geom_smooth(method = lm, 
              color = "magenta", 
              fullrange = T,
              fill = "blue",
              se = TRUE,
              size = 0.5) +
  ggtitle("Dependance of the charges amount on age") +
  labs(x = "Age", y = "Charges") +
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14))
```

<br>
**Despite there's an upward tendensy with age, I don't think there's a sagnifficant difference whether they have kids or not**  

<br>


#Повторение графика
```{r message=FALSE}

#names(wes_palettes)
pal <- wes_palette("GrandBudapest1", 1)


i_c <- insurance_cost %>%
   mutate(
    age_group = case_when(
      age < 35 ~ "21-34",
      age >= 35 & age < 50 ~ "35-49",
      age >= 50 ~ "50+"
    ))
i_c %>%
  ggplot(aes(x = bmi, y = log(charges), color = age_group, fill = age_group, group = age_group)) +
  geom_point(color = pal, alpha = 0.2) +
  facet_grid(.~ age_group) +
  geom_smooth(method=lm,
              alpha = 0.2,
              se=TRUE,
              size = 0.2,
              group = "age_group") +
ggtitle("Отношение индекса массы тела к логарифму трат по возрастным группам") +
theme_minimal() +
theme(legend.position = "bottom")
```

